\makecvtitle

% --------------------------- Education ---------------------------
\section{Education}

\cventry{October 2014}{Master of Science}{Brock University}{St. Catharines}{\textit{Computer Science}}{}

\cventry{October 2011}{Honours Bachelor of Science}{Brock University}{St. Catharines}{\textit{Computer Science}}{Concentration in Software Engineering}

% --------------------------- Experience ---------------------------
\section{Experience}

\subsection{Vocational}

\cventry{April 2014--October 2014}{Software Developer}{Furi Enterprises Inc.}{St. Catharines}{}{
  \begin{itemize}
    \item 
  \end{itemize}
}

\cventry{December 2011--April 2014}{Software Developer Research Associate}{Niagara Research}{Niagara-on-the-Lake}{}{
  \begin{itemize}
    \item determined client needs and create requirements documentation
    \item worked on several 4-8 month long projects
    \item worked with such technologies as c\#, php, objective-c, java, html, css, javascript
    \item worked with libraries and frameworks such as asp.net mvc 3, codeigniter, iphone, android, and laravel.
    \item was given complete control over projects.
    \item worked with gm onstar vehicle sdk and opencar sdk.
  \end{itemize}
}

\cventry{September 2011--April 2012}{Teaching Assistant}{Brock University}{St. Catharines}{Marker-Grader}{
  \begin{itemize}
    \item Lead weekly seminar discussions.
    \item Assisted students at a help desk where they could come ask questions related to material in the course.
    \item Marked assignment submissions.
  \end{itemize}
}

\cventry{January 2012--March 2013}{Freelance Web Developer}{Caters Design Group}{St. Catharines}{}{
  \begin{itemize}
    \item 
  \end{itemize}
}

\cventry{June 2011--April 2012}{Web Developer}{BUSU BrockTV}{St. Catharines}{}{
  \begin{itemize}
    \item 
  \end{itemize}
}

\subsection{Miscellaneous}

\cventry{May 2009--August 2009}{Student Border Services Officer}{Canada Border Services Agency}{Fort Erie}{}{
  \begin{itemize}
    \item Promoted compliance with Canada's border, trade and tax legislation and regulations through responsible enforcement, quality service and education.
    \item Responsible for the interception of drugs, firearms and other prohibited goods from entering Canada.
    \item Assessed duties and taxes on goods entering Canada.
  \end{itemize}
}

\cventry{June 2004--August 2011}{Aquatics Supervisor}{Americana Conference Resort and Spa}{Niagara Falls}{Lifeguard}{
  \begin{itemize}
    \item Supervised up to 14 lifeguards during a shift.
    \item Dealt with high-pressure situations regarding first aid and water safety.
    \item Responsible for addressing patron complaints and concerns.
    \item Responsible for regular pool maintenance and clean up.
  \end{itemize}
}

\cventry{August 2010--August 2011}{Banquet Captain}{Americana Conference Resort and Spa}{Niagara Falls}{Server}{
  \begin{itemize}
    \item Served guests in different functions at the banquet hall.
    \item Coordinate and supervise the execution of banquet functions to ensure the needs of the client are met and that the function runs smoothly and efficiently.
  \end{itemize}
}

% --------------------------- Others ---------------------------

\section{Extra-curricular Involvement}

\cventry{September 2010--August 2011}{President}{Computer Science Club}{Brock University}{}{
  \begin{itemize}
    \item Schedule bi-weekly activities and events.
    \item Maintain Student Chapter of the ACM
    \item Organize teams for the CS Games programming competition in Montreal, Quebec.
    \item Act as a student representative for the Computer Science department.
  \end{itemize}
}

\cventry{October 2010}{Contestant}{ACM International Collegiate Programming Contest}{Windsor, ON}{}{
  \begin{itemize}
    \item Acted as Brock University representative at the East Central North America Regional Contest
  \end{itemize}
}

\cventry{December 2010, 2011}{Teaching Assistant}{Computer Science Fair}{Brock University}{}{
  \begin{itemize}
    \item Assisted Prof. Winter in the `Build your own Space Invaders' workshop.
    \item Lead one of the `Build your own Space Invaders' workshop sessions.
  \end{itemize}
}

\section{Conferences}

\cvitem{}{
  ``Modeling Metal Protein Complexes from Experimental Extended X-ray Absorption Fine Structure using Evolutionary Algorithms'', \textit{Computational Intelligence in Bioinformatics and Computational
Biology.} Honolulu, Hawaii, USA, May 2014.
}

\cvitem{}{
  ``Modeling Metal Protein Complexes from Experimental Extended X-ray Absorption Fine Structure using Evolutionary Algorithms'', \textit{Mapping the New Knowledges Graduate Student Research Conference.} St. Catharines, ON, April 2014.
}

\section{Achievements}

\cventry{September 2009--April 2010}{Exchange Student}{Linnaeus University}{V{\"a}xj{\"o}, Sweden}{}{
  \begin{itemize}
    \item Assisted Prof. Winter in the `Build your own Space Invaders' workshop.
    \item Lead one of the `Build your own Space Invaders' workshop sessions.
  \end{itemize}
}

% \section{Languages}
% \cvitemwithcomment{Language 1}{Skill level}{Comment}
% \cvitemwithcomment{Language 2}{Skill level}{Comment}
% \cvitemwithcomment{Language 3}{Skill level}{Comment}

% \section{Computer skills}
% \cvdoubleitem{category 1}{XXX, YYY, ZZZ}{category 4}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 2}{XXX, YYY, ZZZ}{category 5}{XXX, YYY, ZZZ}
% \cvdoubleitem{category 3}{XXX, YYY, ZZZ}{category 6}{XXX, YYY, ZZZ}

% \section{Interests}
% \cvitem{hobby 1}{Description}
% \cvitem{hobby 2}{Description}
% \cvitem{hobby 3}{Description}

% \section{Extra 1}
% \cvlistitem{Item 1}
% \cvlistitem{Item 2}
% \cvlistitem{Item 3. This item is particularly long and therefore normally spans over several lines. Did you notice the indentation when the line wraps?}

% \section{Extra 2}
% \cvlistdoubleitem{Item 1}{Item 4}
% \cvlistdoubleitem{Item 2}{Item 5\cite{book1}}
% \cvlistdoubleitem{Item 3}{Item 6. Like item 3 in the single column list before, this item is particularly long to wrap over several lines.}
